Model Building

### 2020-07-30 Model_Build.Rmd
Added to Write up and model
Added plot of fitted time series

```{r}
library(tidyverse)
library(fable)
library(lubridate)
library(tsibble)
library(feasts)
```

@@

# picking out and renaming specific variables
# converting date to a month object to fit in fable / tsibble functions
# convert to tsibble
alldata <- combined %>%
  rename(attendance = attendance.x) %>%
  select(-c(year, attendance.y)) %>%
  mutate(date = yearmonth(date)) %>%
  as_tsibble(key = c(team, propTVMarketSize, odds, winpct), index = date)
```

@@

# creating snaive, ets, and arima models
fit <- lad %>%
  model(
    arima = ARIMA(googlehits) # testing with only arima right now
  )

# shows coefficients of the arima models
# Problem with have multiple coefficients
# PROBLEM?? Confused becauses doesnt account for every date so it only creates estimates and models for each unique row (per season)

@@

#forecasted 12 periods into future / do i need to forecast?
# fc <- fit %>%
#   forecast(h = 12)
# 
# fc %>%
#   autoplot(lad, level = NULL)
```

>>>>

```{r}
library(tidyverse)
library(fable)
library(lubridate)
library(tsibble)
library(feasts)
library(mable)
```

@@

# picking out and renaming specific variables
# converting date to a month object to fit in fable / tsibble functions
# convert to tsibble
alldata <- combined %>%
  rename(attendance = attendance.x) %>%
  select(-c(year, attendance.y)) %>%
  mutate(date = yearmonth(date)) %>%
  as_tsibble(key = team, index = date)
```

@@

# creating snaive, ets, and arima models
fit <- lad %>%
  model(
    arima = ARIMA(googlehits ~ odds + attgame + winpct) # testing with only arima right now
  )

# ARIMA is used when implementing exogenous regressors

# DIFFERENT FUNCTIONS TO USE ON MABLE
# augment() grabs fitted values and we can plot these
# glance() checks AIC and BIC
# components() allows us to use ggplot to plot aspects of the model / only works on ets and snaive i think

fitted <- augment(fit)

fitted %>%
  ggplot() + 
  geom_line(aes(x = date, y = googlehits), color = "blue") +
  geom_line(aes(x = date, y = .fitted), color = "red")

# small problem is that it can't produce fitted values for any 2020 months because I don't have winpct for those dates / dont know if it matters?

@@

coef
```
